Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/introduction.tex
Removed confusing footnote in first section.
From reviewer 12:

> The first footnote is confusing. Should the footnote be simply
> embedded into the main text?

This commit removes the footnote and moves the footnote's text into the
main text.

Designing such a general-purpose decision procedure is difficult\footnote{In
fact it's impossible. Determining \invariantconfluence{} of an object is
undecidable in general. Still, we can develop a decision procedure that works
well in the common case.}. Many prior efforts instead develop a decision
procedure for \emph{\invariantclosure{}}, a sufficient (but not necessary)
condition for \invariantconfluence{}~\cite{li2012making, li2014automating}. The
existing approaches check whether an object is \invariantclosed{}. If it is,
then they conclude that it is also \invariantconfluent{}. If it's not, then the
current approaches are unable to conclude anything about whether or not the
object is \invariantconfluent{}.

>>>>

Unfortunately, designing such a general-purpose decision procedure is
impossible because determining the \invariantconfluence{} of an object is
undecidable in general. Still, we can develop a decision procedure that works
well in the common case.
%
For example, many prior efforts have developed decision procedures for
\emph{\invariantclosure{}}, a sufficient (but not necessary) condition for
\invariantconfluence{}~\cite{li2012making, li2014automating}. The existing
approaches check whether an object is \invariantclosed{}. If it is, then they
conclude that it is also \invariantconfluent{}. If it's not, then the current
approaches are unable to conclude anything about whether or not the object is
\invariantconfluent{}.
